Progress 12/3/14
========================================================

Having noticed the genetic algorithm's inabilty to rearrange contigs correctly in it's current form, I have decided to test it with a model genome that has a ratio of homozygous to heterozygous SNP density that is normally distributed. This means I can use R's `qqnorm` to test the distribution for normality, rather than providing a sample distribution for qqplot, as I have been doing (in the fitness method of the genetic algorithm).

If I can prove that the genetic algorithm idea will work in this context, then I can apply the same priciple for real SNP position data, using a more realistic distribution than simply normal (based on what is found in literature.)

```{r}
hm <- rnorm(35, 10000000, 5000000)
remove <- c()
x <- 1
for(i in hm){
  if(i < 0 || i > 18585056){
    remove <- c(remove, x)
  }
  x <- x+1
}
hm <- hm[-c(remove)]

ht <- runif(3000, 1, 18585056)
hmd <- density(hm, from=0, to=18585056)
htd <- density(ht, from=0, to=18585056)
ratio <- hmd$y/htd$y
x <- (1:512)*36298.9375
plot(x,ratio)
```

I have found a problem: I can test `hm` and `ht` with the `shapiro-wilks` test and `qqnorm` and show that `hm` is indeed normally distributed, and `ht` isn't. I don't have a way of testing the density vectors (and by extention the ratio) for normality. What I want is a way of testing normality of ratio. Ideally this method would work out the "normality" for hmd$y in the same way as shapiro and qqnorm do for hm, then this could be applied to the ratio.

```{r}
shapiro.test(hm)
qqp <- qqnorm(hm)
cor(qqp$x,qqp$y)

shapiro.test(hm)
qqp <- qqnorm(hm)
cor(qqp$x,qqp$y)

shapiro.test(hmd$y)
qqp <- qqnorm(hmd$y)
cor(qqp$x,qqp$y)

shapiro.test(ratio)
qqp <- qqnorm(ratio)
cor(qqp$x,qqp$y)
```


```{r}
l <- 18585056
div <- 100#l/10000
breaks <- c(0)
for(i in 1:div){
  breaks <- c(breaks,(l/div)*i)
}
fhm <- summary(cut(hm, breaks))
fht <- summary(cut(ht, breaks))
fratio <- fhm/fht
hm
fhm
fht
fratio

for(f in fratio){
  
}
```
